A Survey of Scientific Workflow Management Systems

### 2014-04-08 paper.tex
cleaning up by removing old workflow descriptions to the bottom. Hopefully will be able to salvage something out of them

@@

%
\paragraph{DaGue/--} Bioflow \cite{bioflow} is a query based workflow language.
It is motivated by the fact that bioinformatics applications are query based
applications that benefit from the complex database queries or saved database
`views'. A typical Bioflow workflow pipelines a sequence of filter queries in
order to get the desired results. Bioflow is mainly utilized in the area of
bioinformatics and querying genome databases. Additionally, a Bioflow workflow
provides mechanisms for data manipulation and updation in the existing
databases. It also includes advanced features such as parallel processing of a
set of mutually independent database queries. The execution model is based on
the popular database query language SQL (Structured Query Language). Processes
can be defined in Bioflow which are processor counterparts in workflow paradigm
and similar to stored-procedures in SQL jargon.

%
\paragraph{*/Martlet} Martlet \cite{martlet} is a text-based, declarative
workflow language that is inspired by the functional programming paradigm. A
Martlet workflow conveniently enables distributed parameter sweep applications
wherein the language intuitively defines the computation and a matching with
the distributed resources can be carried out at workflow execution time. List
processing applications where a sequence of application components work over an
array of data in a Multi-data multi-instruction style setup is well-suited to
the Martlet's model of computation.

%
\paragraph{Knime/--} Knime \cite{knime} is a distributed, parallel pipelining
system for data intensive applications developed at the University of Konstanz.
It is a java-based platform with a Graphical Interface that is based on eclipse
(\textit{http://www.eclipse.org}) plug-in framework. A Knime workflow consists
of processors belonging to categories such as readers, manipulators, learners,
predictors, etc. Each processor has a configuration dialog associated with it
that allows user to set its parameters. Processors are connected through data
and/or control connections. A highlight of knime is support for shared- and
distributed-memory workflow enactment and support for parallel workflow loops
and subworkflows. The loops in Knime manifest themselves in the form of
subworkflows (called metanodes in Knime) by a repeated enactment of the same
subworkflow.
%
\paragraph{*/} StarFlow \cite{angelino-yamins-etal:2010} is a Python-based
script oriented workflow language used to encode parallel pipelines. StarFlow
handles data as well as control flow using a combination of static, dynamic and
user annotations analysis. A parallelization engine uses data and control
dependencies in a workflow in order to build a parallel profile of the
workflow. StarFlow has been shown to be successfully interface with the SunGrid
\cite{gentzsch:2001} Schedular and Amazon EC2 cloud infrastructure \cite{ec2}.
The key feature of StarFlow is its capability to execute workflows to maximum
possible parallelism. While StarFlow provides a script-based compact and
semiautomatic workflow composition environment, currently it lacks a
sophisticated GUI for workflow composition.

@@

\begin{table}[ht!]
\begin{center}
% use packages: array
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
\textbf{SWE} / & \multicolumn{3}{c|}{\textbf{Parallelism}} & \multicolumn{3}{c|}{\textbf{Optimization}}\\
\cline{2-7}
\textbf{Language} & \textbf{data} & \textbf{workflow} & \textbf{pipeline} & \textbf{static} & \textbf{runtime} & \textbf{other}\\ \hline
Taverna/Scufl2 & \checkmark & \checkmark & \checkmark & -- & \checkmark & -- \\\hline
+/BPEL &foreach & \checkmark & -- &-- &\checkmark &-- \\\hline
Triana/- & \checkmark & \checkmark & \checkmark & -- & \checkmark &--\\\hline
MOTEUR/Scufl & \checkmark & \checkmark & \checkmark &-- &\checkmark &-- \\\hline
Kepler/MoML & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark &--\\\hline
GridNexus/GXPL & -- & \checkmark & -- &-- &\checkmark &-- \\\hline
Swift/SwiftScript & \checkmark & \checkmark & \checkmark & \checkmark &\checkmark &-- \\\hline
Askalon/AGWL &--& \checkmark & -- & \checkmark & \checkmark & -- \\\hline
P-GRADE/- &\checkmark &\checkmark &\checkmark &--&--&--\\\hline
Vizbuilder/bioflow &-- &\checkmark &-- &--&\checkmark &Query optimization\\\hline
Martlet/- & \checkmark & \checkmark & -- &-- &\checkmark&-- \\\hline
Knime/- & \checkmark &\checkmark &\checkmark & -- & \checkmark & -- \\\hline
StarFlow/- &\checkmark & \checkmark & \checkmark & \checkmark & \checkmark & -- \\\hline
Pegasus/DAX &\checkmark &\checkmark &\checkmark &\checkmark &\checkmark &AI-based techniques \\\hline
Galaxy/- &-- &-- &\checkmark &-- &-- &-- \\\hline
MOTEUR2/Gwendia~ & \checkmark &\checkmark & \checkmark &-- &\checkmark &-- \\\hline
\end{tabular}
%\caption{A summary of SWEs Scalability and optimization Mechanisms}
\label{tbl:scalability}
\end{center}
\end{table}

@@

% ---------------------------------------------------------------------------

>>>>

3. GeMTC project investigating running many-task applications over GPUs via Swift/T.

@@

%
\paragraph{DaGue/--}

%

@@

\begin{table}[ht!]
\begin{center}
% use packages: array
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
\textbf{SWE} / & \multicolumn{3}{c|}{\textbf{Parallelism}} & \multicolumn{3}{c|}{\textbf{Optimization}}\\
\cline{2-7}
\textbf{Language} & \textbf{data} & \textbf{workflow} & \textbf{pipeline} & \textbf{static} & \textbf{runtime} & \textbf{other}\\ \hline
Taverna/Scufl2 & \checkmark & \checkmark & \checkmark & -- & \checkmark & -- \\\hline
+/BPEL &foreach & \checkmark & -- &-- &\checkmark &-- \\\hline
Triana/- & \checkmark & \checkmark & \checkmark & -- & \checkmark &--\\\hline
MOTEUR/Scufl & \checkmark & \checkmark & \checkmark &-- &\checkmark &-- \\\hline
Kepler/MoML & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark &--\\\hline
GridNexus/GXPL & -- & \checkmark & -- &-- &\checkmark &-- \\\hline
Swift/SwiftScript & \checkmark & \checkmark & \checkmark & \checkmark &\checkmark &-- \\\hline
Askalon/AGWL &--& \checkmark & -- & \checkmark & \checkmark & -- \\\hline
P-GRADE/- &\checkmark &\checkmark &\checkmark &--&--&--\\\hline
Vizbuilder/bioflow &-- &\checkmark &-- &--&\checkmark &Query optimization\\\hline
Pegasus/DAX &\checkmark &\checkmark &\checkmark &\checkmark &\checkmark &AI-based techniques \\\hline
Galaxy/- &-- &-- &\checkmark &-- &-- &-- \\\hline
MOTEUR2/Gwendia~ & \checkmark &\checkmark & \checkmark &-- &\checkmark &-- \\\hline
\end{tabular}
%\caption{A summary of SWEs Scalability and optimization Mechanisms}
\label{tbl:scalability}
\end{center}
\end{table}

@@

%
Bioflow \cite{bioflow} is a query based workflow language.
It is motivated by the fact that bioinformatics applications are query based
applications that benefit from the complex database queries or saved database
`views'. A typical Bioflow workflow pipelines a sequence of filter queries in
order to get the desired results. Bioflow is mainly utilized in the area of
bioinformatics and querying genome databases. Additionally, a Bioflow workflow
provides mechanisms for data manipulation and updation in the existing
databases. It also includes advanced features such as parallel processing of a
set of mutually independent database queries. The execution model is based on
the popular database query language SQL (Structured Query Language). Processes
can be defined in Bioflow which are processor counterparts in workflow paradigm
and similar to stored-procedures in SQL jargon.

\paragraph{*/Martlet} Martlet \cite{martlet} is a text-based, declarative
workflow language that is inspired by the functional programming paradigm. A
Martlet workflow conveniently enables distributed parameter sweep applications
wherein the language intuitively defines the computation and a matching with
the distributed resources can be carried out at workflow execution time. List
processing applications where a sequence of application components work over an
array of data in a Multi-data multi-instruction style setup is well-suited to
the Martlet's model of computation.

%
\paragraph{Knime/--} Knime \cite{knime} is a distributed, parallel pipelining
system for data intensive applications developed at the University of Konstanz.
It is a java-based platform with a Graphical Interface that is based on eclipse
(\textit{http://www.eclipse.org}) plug-in framework. A Knime workflow consists
of processors belonging to categories such as readers, manipulators, learners,
predictors, etc. Each processor has a configuration dialog associated with it
that allows user to set its parameters. Processors are connected through data
and/or control connections. A highlight of knime is support for shared- and
distributed-memory workflow enactment and support for parallel workflow loops
and subworkflows. The loops in Knime manifest themselves in the form of
subworkflows (called metanodes in Knime) by a repeated enactment of the same
subworkflow.
%
\paragraph{*/} StarFlow \cite{angelino-yamins-etal:2010} is a Python-based
script oriented workflow language used to encode parallel pipelines. StarFlow
handles data as well as control flow using a combination of static, dynamic and
user annotations analysis. A parallelization engine uses data and control
dependencies in a workflow in order to build a parallel profile of the
workflow. StarFlow has been shown to be successfully interface with the SunGrid
\cite{gentzsch:2001} Schedular and Amazon EC2 cloud infrastructure \cite{ec2}.
The key feature of StarFlow is its capability to execute workflows to maximum
possible parallelism. While StarFlow provides a script-based compact and
semiautomatic workflow composition environment, currently it lacks a
sophisticated GUI for workflow composition. 
% ---------------------------------------------------------------------------
